Mixed effect tweedie model in TMB

### 2020-02-24 analysis/tmb-sensor-explore/2-fit-temperature.Rmd
misc inconsequential

```{r}
library(gbm)

@@

## Just compare fixed slope models with simplest random effect structure
```{r}
cv_args <- generate_cv_args(
  formula = list(
    temperature_c ~ 0 + SST_scaled*shallow + depth_scaled,
    temperature_c ~ 0 + SST_scaled*shallow + depth_scaled + depth_scaled2,
    temperature_c ~ 0 + SST_scaled*shallow + depth_scaled + depth_scaled2 + depth_scaled3,
    temperature_c ~ 1 + SST_scaled + depth_scaled,
    temperature_c ~ 1 + SST_scaled + depth_scaled + depth_scaled2,
    temperature_c ~ 1 + SST_scaled + depth_scaled + depth_scaled2 + depth_scaled3,
    temperature_c ~ 0 + as.factor(year) + depth_scaled,
    temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2,
    temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2 + depth_scaled3,
    temperature_c ~ 0 + as.factor(year) + SST_scaled + depth_scaled,
    temperature_c ~ 0 + as.factor(year) + SST_scaled + depth_scaled + depth_scaled2,
    temperature_c ~ 0 + as.factor(year) + SST_scaled + depth_scaled + depth_scaled2 + depth_scaled3,
    temperature_c ~ 0 + as.factor(year) + SST_scaled * depth_scaled,
    temperature_c ~ 0 + as.factor(year) + SST_scaled * depth_scaled + SST_scaled * depth_scaled2,
    temperature_c ~ 0 + as.factor(year) + SST_scaled * depth_scaled + SST_scaled * depth_scaled2 + SST_scaled * depth_scaled3
  ),
  time_varying = list(NULL),
  ar1_fields = c(FALSE),
  include_spatial = c(FALSE),
  n_knots = c(100),
  seed = c(1111, 2222, 3333, 4444)
)

@@

## Compare time-varying slope models still with simplest random effect structure
All of top models for any seed contained year and none showed a linear effect of depth
All are better than fixed slope models
```{r}
cv_args <- generate_cv_args(
  formula = list(
    #temperature_c ~ 0 + SST_scaled*shallow,
    temperature_c ~ 0 + as.factor(year) + SST_scaled*shallow,
    #temperature_c ~ 1 + SST_scaled,
    temperature_c ~ 0 + as.factor(year) + SST_scaled,
    temperature_c ~ 0 + as.factor(year)
  ),
  time_varying = list(
    ~ 0 + depth_scaled + depth_scaled2,
    ~ 0 + depth_scaled + depth_scaled2 + depth_scaled3
  ),
  ar1_fields = c(FALSE),
  include_spatial = c(FALSE),
  n_knots = c(100), # keep same n_knots
  seed = c(1111, 2222, 3333, 4444) # keep same seeds
)

>>>>

```{r eval = FALSE}
library(gbm)

@@

## Just compare fixed slope models with simplest random effect structure
```{r eval=F}
cv_args <- generate_cv_args(
  formula = list(
    temperature_c ~ 0 + SST_scaled*shallow + depth_scaled,
    temperature_c ~ 0 + SST_scaled*shallow + depth_scaled + depth_scaled2,
    temperature_c ~ 0 + SST_scaled*shallow + depth_scaled + depth_scaled2 + depth_scaled3,
    temperature_c ~ 1 + SST_scaled + depth_scaled,
    temperature_c ~ 1 + SST_scaled + depth_scaled + depth_scaled2,
    temperature_c ~ 1 + SST_scaled + depth_scaled + depth_scaled2 + depth_scaled3,
    temperature_c ~ 0 + as.factor(year) + depth_scaled,
    temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2,
    temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2 + depth_scaled3,
    temperature_c ~ 0 + as.factor(year) + SST_scaled + depth_scaled,
    temperature_c ~ 0 + as.factor(year) + SST_scaled + depth_scaled + depth_scaled2,
    temperature_c ~ 0 + as.factor(year) + SST_scaled + depth_scaled + depth_scaled2 + depth_scaled3,
    temperature_c ~ 0 + as.factor(year) + SST_scaled * depth_scaled,
    temperature_c ~ 0 + as.factor(year) + SST_scaled * depth_scaled + SST_scaled * depth_scaled2,
    temperature_c ~ 0 + as.factor(year) + SST_scaled * depth_scaled + SST_scaled * depth_scaled2 + SST_scaled * depth_scaled3
  ),
  time_varying = list(NULL),
  ar1_fields = c(FALSE),
  include_spatial = c(FALSE),
  n_knots = c(100),
  seed = c(1111, 2222, 3333, 4444)
)

@@

## Compare time-varying slope models still with simplest random effect structure
All of top models for any seed contained year and none showed a linear effect of depth
All are better than fixed slope models
```{r}
cv_args <- generate_cv_args(
  formula = list(
    #temperature_c ~ 0 + SST_scaled*shallow,
    # temperature_c ~ 0 + as.factor(year) + SST_scaled*shallow,
    # #temperature_c ~ 1 + SST_scaled,
    # temperature_c ~ 0 + as.factor(year) + SST_scaled,
    temperature_c ~ 0 + as.factor(year)
  ),
  time_varying = list(
    # ~ 0 + depth_scaled + depth_scaled2 + depth_scaled3,
    ~ 0 + depth_scaled + depth_scaled2,
  ),
  ar1_fields = c(TRUE),
  include_spatial = c(TRUE),
  n_knots = c(400), # keep same n_knots
  seed = c(1111, 2222, 3333, 4444) # keep same seeds
)
